MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-03-13 MAESTROeX_I/intro.tex
more intro

In this paper, we characterize the performance of the MAESTROeX algorithm compared to the previous implementation.
We also develop simpler, alternative temporal integrators, with a longer term goal of developing high-order coupling schemes.
We also present a new treatment of the base state mapping to Cartesian grids for spherical problems.

>>>>

We also present new algorithmic methodology that improves upon Paper V in a number of ways.
First, the overall temporal algorithm has been greatly simplified without compromising accuracy.
The key design decision was to replace the predicted evolution of the base state with 
a predictor-corrector approach.  Not only does this greatly simplify the dynamics of the base
state, but this treatment is more amenable to higher-order multiphysics coupling strategies
based on method-of-lines integration.  Second, we now provide additional spatial mapping
procedures that reduces, and in some cases eliminates, mapping error from the one-dimensional
base state to the Cartesian grid state for spherical problems.
Finally, the code has been completely ported to a new software framework suitable for modern manycore supercomputers.
The resulting MAESTROeX is implemented in the C++/F90 AMReX software library.  MAESTROeX uses MPI+OpenMP parallelism
and scales to XXX MPI processes, each capable of spawning tens of threads.
\MarginPar{quantify XXX.  I think it's 5,000-10,000 MPIs with potentially hundreds of threads}
